{ \fontfamily{ptm}\selectfont Catalyst Meta Acceleration Framework: The history and the gist of it }

### 2024-12-07 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

\appendix
\section{Theorems and claims for accelerated proximal gradient}\label{app:sec:thm-claim-acc-prox-grad}
    Throughout this section, $F = g + f$ is an additive composite objective function with $g$ convex, $f$ $L$-lipschitz smooth and $\mu \ge0$ strongly convex. 
    The notations here are 
    \begin{align*}
        \mathcal M^{L^{-1}}(x; y),
        &:= 
        F(x) + \frac{L}{2}\Vert x - y\Vert^2,
        \\
        \widetilde{ \mathcal M}^{L^{-1}}(x; y) ,
        &:= g(x) + f(y) 
        + 
        \left\langle \nabla f(x), x - y\right\rangle 
        + 
        \frac{L}{2}\Vert x - y\Vert^2,
        \\
        \widetilde{\mathcal J}_{L^{-1}}y 
        &:= \argmin_{x} \widetilde{\mathcal M}^{L^{-1}}(x; y),
        \\
        \widetilde{\mathcal G}_{L^{-1}}(y)
        &:= L\left(I - \widetilde{\mathcal J}_{L^{-1}}\right)y. 
    \end{align*}
    We also introduce Bregman Divergence. 
    Let $h: Q \rightarrow \RR$ be a differentiable smooth convex function on a closed convex domain $Q \subseteq \RR^n$.
    Define 
    $$
        D_h: Q \times \reli Q \rightarrow \RR^n
        := (x, y) \mapsto h(x) - h(y) - \langle \nabla h(y), x - y\rangle. 
    $$

@@

        Therefore it gives: 

@@

\section{Proofs for Catalyst Meta Acceleration}
    In this section, we prove the inexact proximal inequality and give the Nesterov's estimating sequence void of intractable quantities. 
    The notation is the same as
    \hyperref[sec:lin-2015]{Section \ref*{sec:lin-2015}}. 
    Recall inexact evaluation $x_k \approx \mathcal J_{\kappa^{-1}}y_{k - 1}$ such that $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}}y_{k - 1}; y_{k - 1}) \le \epsilon_k$; $x_k^* = \mathcal J_{\kappa^{-1}}y_{k - 1}$ to be the exact evaluation.

@@

            \textcolor{gray}{

@@

                \tilde x_k &= x_{k - 1} + \alpha_k(v_k - x_{k - 1})

>>>>

\appendix
\section{Theorems and claims for accelerated proximal gradient}\label{app:sec:thm-claim-acc-prox-grad}
    Throughout this section, $F = g + f$ is an additive composite objective function with $g$ convex, $f$ $L$-Lipschitz smooth and $\mu \ge0$ strongly convex. 
    The notations here are 
    \begin{align*}
        \mathcal M^{L^{-1}}(x; y),
        &:= 
        F(x) + \frac{L}{2}\Vert x - y\Vert^2,
        \\
        \widetilde{ \mathcal M}^{L^{-1}}(x; y) ,
        &:= g(x) + f(y) 
        + 
        \left\langle \nabla f(x), x - y\right\rangle 
        + 
        \frac{L}{2}\Vert x - y\Vert^2,
        \\
        \widetilde{\mathcal J}_{L^{-1}}y 
        &:= \argmin_{x} \widetilde{\mathcal M}^{L^{-1}}(x; y),
        \\
        \widetilde{\mathcal G}_{L^{-1}}(y)
        &:= L\left(I - \widetilde{\mathcal J}_{L^{-1}}\right)y. 
    \end{align*}
    We also introduce Bregman Divergence. 
    Let $h: Q \rightarrow \RR$ be a differentiable smooth convex function on a closed convex domain $Q \subseteq \RR^n$.
    Define 
    $$
        D_h: Q \times \inte Q \rightarrow \RR^n
        := (x, y) \mapsto h(x) - h(y) - \langle \nabla h(y), x - y\rangle. 
    $$

@@

        Therefore, it gives: 

@@

\section{Proofs for Catalyst Meta Acceleration}
    In this section, we prove the inexact proximal inequality and give the Nesterov's estimating sequence without intractable quantities. 
    The notation is the same as
    \hyperref[sec:lin-2015]{Section \ref*{sec:lin-2015}}. 
    Recall inexact evaluation $x_k \approx \mathcal J_{\kappa^{-1}}y_{k - 1}$ such that $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}}y_{k - 1}; y_{k - 1}) \le \epsilon_k$; $x_k^* = \mathcal J_{\kappa^{-1}}y_{k - 1}$ to be the exact evaluation.

@@

        On the first equality after $x - \tilde x_k$, we substituted $\tilde x_k$ using the definition of the algorithm which is 

@@

            \tilde x_k &= x_{k - 1} + \alpha_k(v_k - x_{k - 1}). 
